---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# libminer

<!-- badges: start -->
[![R-CMD-check](https://github.com/plandahl/libminer/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/plandahl/libminer/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of libminer is to provide an overview ofyour R Library setup.
This is a test package created as part of a workshop.

## Installation

You can install the development version of libminer from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("plandahl/libminer")
```

## Example

To get a count of installed packages in each of your libraries use `lib_summary()`
This is a basic example which shows you how to solve a common problem:

```{r example}
library(libminer)

lib_summary()
lib_summary(TRUE)

```
